Resumé title

### 2017-06-29 paper/coverletter.tex
Point to figure

% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{classic}
% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{green}
% to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\renewcommand{\familydefault}{\sfdefault}
% uncomment to suppress automatic page numbering for CVs longer than one page
%\nopagenumbers{}

@@

% personal data
\name{Semyeong}{Oh}
\title{Resumé title}
\address{4 Ivy Ln}{Princeton, NJ 08540}{United States}
\email{semyeong@astro.princeton.edu}

@@

% recipient data
\recipient{Dr. Leslie Sage}{968 National Press Building\\529 14th Street NW\\Washington DC 20045-1938\\United States}
\date{\today}
\opening{Dear Dr. Sage,}
\closing{Best regards,}
\makelettertitle

We submit the enclosed document for consideration for a Nature Letter.
The paper lays out a simple and clear account for evidences in stellar
chemical abundances that massive rocky accretion happened in one of the two
stars that are comoving in space, and possibly also in the other one albeit in
smaller amount.
We think the result is one of the most convincing examples that shows a
catastrophic ending possible to planets around sun-like stars, and thus will be
interesting to scientists in other disciplines as well as those in astronomy or
exoplanet field.

>>>>

% moderncv themes
% style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvstyle{classic}
% color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\moderncvcolor{green}

@@

% personal data
\name{Semyeong}{Oh}
\address{4 Ivy Ln}{Princeton, NJ 08540}{United States}
\email{semyeong@astro.princeton.edu}

@@

% recipient data
\recipient{Dr. Leslie Sage}{
  968 National Press Building\\
  529 14th Street NW\\
  Washington DC 20045-1938\\
  United States}
\date{\today}
\opening{Dear Dr. Sage,}
\closing{Best regards,}
\makelettertitle

We submit the enclosed paper for consideration for a Nature Letter.
The paper lays out a simple and clear account for evidences in stellar
chemical abundances that massive rocky accretion happened in one of the two
stars that are comoving in space, and possibly also in the other one albeit in
smaller amount. Figure~2 demonstrates this key result where we compare
the abundance difference between the two stars with the change
expected from accretion of bulk Earth by a sun-like star.
We think the result is one of the most convincing examples that shows a
catastrophic ending possible to planets around sun-like stars, and thus will be
interesting to scientists in other disciplines as well as those in astronomy or
exoplanet field.
